---
title: "Helpline Quarterly Report"
author: "Anita Blackstaffe"
date: "24/03/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(janitor)
```

```{r, include=FALSE}
# Import full crisis dataset
crisis <- read_csv("data/_Data_Crisis Line_2020-01-01 to 2020-10-31.csv")
View(crisis)
```

```{r, include=FALSE}
# Import full info line dateset
info <- read_csv("data/_Data_Info Line_2020-01-01 to 2020-09-30.csv")
View(info)
```

# Introduction

The Help Centre provides monthly data from two sources:

 1. Calls/Texts/Chats to the **Information Line**
 1. Calls/Texts/Chats to the **Crisis Line**

This report gives an overview of data from these two sources for the period **January 1, 2020 to March 31, 2020**.

### Contents of Report

1. Number of Contacts
1. Overall Demographics of Contacts
1. COVID-19 Related Contacts
1. Needs and Concerns 
1. Special Needs and Concerns during COVID-19
       
```{r, include=FALSE}
# Create new dataframe for Q1 crisis data only
crisis_Q1 <- crisis %>%
    filter(month <= 3)
View(crisis_Q1)
```

```{r, include=FALSE}
# Create new dataframe for Q1 info data only
info_Q1 <- crisis %>%
    filter(month <= 3)
View(info_Q1)
```

# Number of Contacts

### Information Line Contacts

```{r}
# Frequencies for number of info line contacts per month (Q1)
info_Q1 %>%
    tabyl(month) %>%
    adorn_pct_formatting(digits=1, rounding="half up")
```

### Crisis Line Contacts

```{r}
# Frequencies for number of crisis line contacts per month (Q1)
crisis_Q1 %>%
    tabyl(month) %>%
    adorn_pct_formatting(digits=1, rounding="half up")
```


# Overall Demographics

### Gender of Information Line Contacts

```{r}
# Gender of Contacts
info_Q1 %>%
    tabyl(Gender) %>%
    adorn_pct_formatting(digits=1, rounding="half up")
```


### Gender of Crisis Line Contacts

```{r}
# Gender of Contacts
crisis_Q1 %>%
    tabyl(Gender) %>%
    adorn_pct_formatting(digits=1, rounding="half up")
```
